\section{Introduction}

\subsection{Purpose}

\textit{Sleepy Files} (SF) is meant to limit the amount of time a file can be kept open each day by refusing subsequent attempts to open the file. The idea is a simplified version of giving ownership of files to specific programs. The two ideas share the following characteristics: a process can be allowed or denied the ability to open a particular file, and relevant information is stored in file's extended attributes.

If a file is open longer than a set time, all the processes with it already open are allowed to keep it open. If any process attempts another open on the same file, then a \textit{Operation Not Permitted} error is returned.

As soon as the computer clock passes midnight then any previous total open time on files is ignored, and the total open time is set back to 0. Thus, whenever a new day starts, files can be opened again for their allotted amount of time.

\subsection{Design}

To store all the data required to determine whether or not a file can be opened, extended attributes are used. Extended attributes are, essentially, key-value pairs which can be stored on individual files; thus, all the information for one file is stored with that file.

To track how long a file is open, a value is stored as the \textit{Total Open Time} (TOT) (i.e. the time for which any already closed file was open for). A value also stores the current number of opens, \textit{Open Count} (OC), for a file (i.e. the number of times the file has been opened without being closed). Finally, a value stores the time at which the first open was performed, \textit{First Open Time} (FOT), (i.e. the time at which an open was performed when the OC was zero).

Every time a file is opened, SF checks if the file has been open for too long. A file is considered to be opened for too long if either the TOT is greater than the \textit{Open Limit} (OL), where the OL is an arbitrarily long span of time, or the file is already open and the current time minus the FOT plus the TOT is greater than the OL.

If SF has determined that the file has not been open for too long, the OC is incremented by 1. If the file was opened when the OC was zero, then the FOT is set on the file to the current time.

During the closing of a file, the OC is decremented by 1. If the OC is decremented to 0, then the TOT is updated to be the result of the current TOT plus the current time minus the FOT.